% !TEX program = xelatex
% BNPL Agentic Pod — Master Implementation Plan
% Compile with: xelatex MASTERPLAN.tex  (twice for TOC)
% Overleaf: set compiler to XeLaTeX in Menu → Compiler.

\documentclass[11pt]{article}

\usepackage[letterpaper,margin=0.95in]{geometry}
\usepackage{fontspec}
\usepackage{amsmath,amssymb}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{longtable,booktabs,array}
\usepackage{xcolor}
\usepackage[hidelinks,colorlinks=true,linkcolor=black,urlcolor=blue!55!black]{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{listings}

% Fonts — DejaVu has excellent Unicode/symbol coverage (Greek, math ops, arrows, etc.).
% Upload the ./fonts/ directory alongside this .tex file on Overleaf (or keep it beside
% the .tex file locally). The TTFs are loaded by filename so no system install is needed.
\setmainfont{DejaVuSerif.ttf}[
  Path          = ./fonts/ ,
  BoldFont      = DejaVuSerif-Bold.ttf ,
  ItalicFont    = DejaVuSerif-Italic.ttf ,
  BoldItalicFont= DejaVuSerif-BoldItalic.ttf ,
  Scale         = 0.95 ]
\setsansfont{DejaVuSans.ttf}[
  Path          = ./fonts/ ,
  BoldFont      = DejaVuSans-Bold.ttf ,
  ItalicFont    = DejaVuSans-Oblique.ttf ,
  BoldItalicFont= DejaVuSans-BoldOblique.ttf ,
  Scale         = 0.92 ]
\setmonofont{DejaVuSansMono.ttf}[
  Path          = ./fonts/ ,
  BoldFont      = DejaVuSansMono-Bold.ttf ,
  ItalicFont    = DejaVuSansMono-Oblique.ttf ,
  BoldItalicFont= DejaVuSansMono-BoldOblique.ttf ,
  Scale         = 0.85 ]
% Math: default Computer Modern math (works everywhere, including bare MiKTeX).

\setlength{\parskip}{4pt plus 1pt}
\setlength{\parindent}{0pt}
\setlist{topsep=2pt,itemsep=1pt,parsep=0pt}

% Heading styles
\titleformat{\section}{\sffamily\Large\bfseries}{\thesection.}{0.6em}{}[\vspace{-6pt}\rule{\textwidth}{0.4pt}]
\titleformat{\subsection}{\sffamily\large\bfseries}{\thesubsection}{0.6em}{}
\titleformat{\subsubsection}{\sffamily\normalsize\bfseries}{\thesubsubsection}{0.6em}{}

% Footer
\pagestyle{fancy}\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\sffamily\footnotesize BNPL Agentic Pod — Master Implementation Plan \quad\textbullet\quad \thepage\ / \pageref{LastPage}}
\usepackage{lastpage}

% Code listings
\definecolor{codebg}{HTML}{F5F5F5}
\definecolor{codeborder}{HTML}{CCCCCC}
\lstset{
  basicstyle=\ttfamily\footnotesize,
  backgroundcolor=\color{codebg},
  frame=single,
  framesep=4pt,
  rulecolor=\color{codeborder},
  breaklines=true,
  breakatwhitespace=false,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  xleftmargin=4pt,
  xrightmargin=4pt,
}

\newcommand{\inlinecode}[1]{{\ttfamily\small #1}}

\title{\sffamily\bfseries\Huge BNPL Agentic Pod\\[2pt]\Large Master Implementation Plan}
\author{\sffamily Class 580, Spring 2026 \quad\textbullet\quad Depth-first, no timeline}
\date{\sffamily April 17, 2026}

\begin{document}

\maketitle

\noindent\textbf{Purpose of this document.} This is a complete, self-contained handoff brief. Paste it into a fresh Claude Opus session (or any frontier model) and the model will have everything required to continue the project without access to the prior Sonnet conversation: the thesis, the decided architecture, the locked technology stack, the repo layout, the sprint-by-sprint implementation sequence, the rigor requirements, the known traps, and the verification criteria.

\noindent\textbf{Author context.} Student, class 580, Spring 2026, solo, local machine + NVIDIA NIM credits + Claude API. Active F\&O trader. Broad technical background, not deep in any one area --- wants opinionated library-level guidance, not concept-level hand-waving. Dropped the original 17-day timeline on 2026-04-17; now depth-first, targeting institutional rigor (``Nobel Prize level'' in the user's words) equivalent to or exceeding \href{https://github.com/shreejitverma/Adaptive-Volatility-Regime-Based-Execution-and-Risk-Framework}{\texttt{github.com/shreejitverma/Adaptive-Volatility-Regime-Based-Execution-and-Risk-Framework}}.

\noindent\textbf{Two artifacts, equal weight.}
\begin{enumerate}
  \item A running multi-agent AI pod that continuously ingests data, runs analyses, executes backtests, and emits trading strategy / reports autonomously.
  \item An institutional-grade research paper kept in-sync with the pod's empirical output. Current state: \inlinecode{PRELIMINARY\_PAPER.md} (\textasciitilde10{,}000 words, version 0.1, methodology-complete, empirical-pending).
\end{enumerate}

\tableofcontents
\vspace{1em}\hrule\vspace{1em}

\section{The Thesis in One Paragraph}

Buy-Now-Pay-Later lending is a structurally hidden consumer-credit stack. Micro-loans under \textasciitilde\$500 are not reported to Experian/Equifax/TransUnion, so loan-stacking (\textasciitilde63\% of BNPL borrowers per CFPB 2023) is invisible to FICO and by extension to the underwriting of every lender above BNPL in the consumer's capital stack. This produces a \emph{leading-vs-reported} asymmetry: alternative-data streams (CFPB complaints, Reddit distress sentiment, Google Trends on keywords like ``can't afford Affirm,'' MOVE index for fixed-income funding stress) move \emph{before} the AFRMMT trustee reports show roll-rate acceleration and excess-spread compression. The thesis is that a composite of these alternative streams (the \textbf{BSI}) Granger-causes AFRMMT stress at 4--8 week lags, and that the correct trade is a \textbf{Total Return Swap (TRS) Payer position on junior tranches of Affirm Master Trust securitizations} --- not an equity short on AFRM/SQ/PYPL, because those are squeeze-vulnerable. The trade fires only when four orthogonal gates agree ($\mathrm{BSI} \wedge \mathrm{SCP} \wedge \mathrm{MOVE}>120 \wedge \mathrm{CCD\text{-}II\text{-}proximity}$).

\section{Locked Architectural Decisions}

These were debated and resolved during the planning session. Do not relitigate without cause.

{\small
\begin{longtable}{@{}p{3.2cm} p{4.8cm} p{7.5cm}@{}}
\toprule
\textbf{Decision} & \textbf{Choice} & \textbf{Reason} \\
\midrule
\endhead
ABS pricing model & \textbf{Jarrow-Turnbull reduced-form}, dynamic $\lambda(t) = \lambda_0 \cdot \exp(\beta_{\mathrm{BSI}} \mathrm{BSI} + \beta_{\mathrm{MOVE}} \mathrm{MOVE} + \beta_{\mathrm{ES}} \mathrm{compression})$ & Original spec conflated Heston with ABS pricing. Heston is for equity options. Correct credit-derivatives model for tranche pricing is reduced-form intensity (Jarrow-Turnbull 1995, Duffie-Singleton 1999). \\
Heston usage & \textbf{Equity signal layer only} (AFRM/SQ options $\to$ SCP metric) & Never on ABS. Heston $\ne$ credit model. \\
Portfolio optimization & \textbf{CVXPY Mean-CVaR (primary)}; cuOpt only for routing/cardinality/turnover/integer & cuOpt is combinatorial --- not a natural solver for continuous Mean-CVaR. $160\times$ speed claim is irrelevant at $<100$ assets. Using cuOpt for CVaR is a known trap. \\
LLM hosting & \textbf{NVIDIA NIM hosted Nemotron} (\inlinecode{integrate.api.nvidia.com/v1}, OpenAI-compatible) with \textbf{Claude API fallback} via unified \inlinecode{llm\_client.py} & No GPU infra. User has NIM credits. TensorRT-LLM self-hosting out of scope. \\
Model tiering & \textbf{Nemotron-small} for Data/Macro (structured parsing); \textbf{Nemotron-4-340B} for Quant/Risk Manager (complex reasoning) & Latency/cost vs.\ reasoning depth. \\
Agent framework & \textbf{LangGraph} + \textbf{NVIDIA NeMo Agent Toolkit} (observability, tool persistence, audit trail) & NeMo Agent Toolkit replaces what the original spec called ``AI-Q.'' Audit trail is required for the paper's reproducibility appendix and the Human-in-the-Loop approve-trade UX. \\
Vector store & \textbf{Milvus} with \textbf{NV-EmbedQA} embeddings & Local, keeps data in repo, replaces OpenAI embeddings for SEC/CFPB/AFRMMT document RAG. \\
Data warehouse & \textbf{DuckDB} single-file & Zero-config, analytics-fast, no Postgres daemon. \\
Data sources & Tier A free only: FRED, SEC EDGAR (\inlinecode{efts.sec.gov} public API, 10 req/s, \textbf{no proxies}), CFPB Complaint DB, Reddit PRAW, Google Trends via \inlinecode{pytrends}, FINRA short-interest, yfinance/CBOE options & Tier B/C framed as ``plug your Tier C data in for $3\times$ amplification.'' No residential proxies. No App Store scraping. \\
Earnings-call ASR & \textbf{NVIDIA Parakeet-CTC} for real-time transcription $\to$ Macro Agent tone/keyword extraction & Genuine alpha signal on earnings days. \\
Dashboard & \textbf{Streamlit first}, port to \textbf{Next.js + WebSockets} once core works & Streamlit = fast first-pass; Next.js = institutional-polish final. \\
Paper format & \textbf{LaTeX}, hedge-fund-white-paper style (Tufte-like), Chicago author-date citations & Class format not specified; LaTeX is default institutional. \\
NLP sentiment & \textbf{FinBERT} (Araci 2019) primary, \textbf{FinBERT-tone} (Yang et al.\ 2020) robustness & Both HuggingFace, commodity. \\
Execution & \textbf{Simulated TRS P\&L only}. No brokerage integration. & Thesis does not depend on live execution. \\
\bottomrule
\end{longtable}
}

\section{The Four-Gate Trade Logic (Non-Negotiable)}

A trade fires \textbf{only} when all four gates agree:

\begin{enumerate}
  \item \textbf{Gate 1 (BSI, weekly, leading):} BSI z-score $>$ threshold. Default composite: $0.25 \cdot \mathrm{CFPB} + 0.20 \cdot \mathrm{GoogleTrends} + 0.20 \cdot \mathrm{Reddit}_{\mathrm{FinBERT}} + 0.15 \cdot \mathrm{AppStore} + 0.20 \cdot \mathrm{MOVE}$. Weights refined by constrained QP regression against AFRMMT ground truth (simplex constraint, $\sum w = 1$, $w \ge 0$).
  \item \textbf{Gate 2 (SCP, per-asset):} Heston Expected Shortfall minus GBM Expected Loss --- wide gap $=$ equity mispricing tail risk. Equity signal layer only.
  \item \textbf{Gate 3 (MOVE, macro):} ICE BofA MOVE Index 30-day MA $>$ 120 (funding stress regime).
  \item \textbf{Gate 4 (CCD II calendar):} EU Consumer Credit Directive II compliance deadline Nov 2026 within trade horizon.
\end{enumerate}

The \textbf{Risk Manager agent} vetoes any trade where fewer than four gates fire. The \textbf{Squeeze Defense Layer} is an additional veto on equity expressions (utilization $>$ 85\%, days-to-cover $>$ 5, 25-$\delta$ IV skew elevated). Structured-credit TRS expression bypasses squeeze defense.

\section{Repository Layout}

\begin{lstlisting}
bnpl-pod/
├── README.md
├── Makefile                        # make ingest | bsi | validate | backtest | paper | pod | dashboard
├── pyproject.toml                  # uv/poetry managed
├── .env.example
├── docker-compose.yml              # Milvus service
├── config/
│   ├── weights.yaml                # BSI weights, refined by QP after calibration
│   └── thresholds.yaml             # gate thresholds, squeeze-defense thresholds
├── data/
│   ├── ingest/
│   │   ├── fred.py                 # FRED API (MOVE, 10Y-3M, CC delinq, SOFR)
│   │   ├── sec_edgar.py            # efts.sec.gov search API, not scraper
│   │   ├── abs_parser.py           # AFRMMT 10-D / ABS-15G -> roll rate, excess spread, CNL
│   │   ├── cfpb.py                 # CFPB public Complaint Database API
│   │   ├── reddit_praw.py          # r/povertyfinance, r/Debt, r/personalfinance, r/Affirm
│   │   ├── google_trends.py        # pytrends, keyword set K
│   │   ├── options_chain.py        # yfinance or CBOE free feed
│   │   ├── short_interest.py       # FINRA public short-interest
│   │   └── earnings_audio.py       # fetch earnings-call audio, Parakeet transcription
│   └── warehouse.duckdb
├── nlp/
│   ├── finbert_sentiment.py        # HF pipeline, rolling 30-day negative ratio
│   ├── finbert_tone.py             # robustness classifier
│   ├── embed_nvemb.py              # NV-EmbedQA via NIM
│   └── rag/
│       ├── milvus_store.py
│       └── ingest_docs.py          # index AFRMMT PDFs, 10-Qs, CFPB rules
├── signals/
│   ├── bsi.py                      # weighted z-score composite
│   ├── weights_qp.py               # constrained QP for weight refinement
│   ├── granger.py                  # statsmodels + block bootstrap
│   └── rolling_oos.py              # rolling-window OOS backtest of the signal
├── quant/
│   ├── jarrow_turnbull.py          # dynamic lambda(t), Monte Carlo survival, tranche pricing
│   ├── heston_scp.py               # QuantLib Heston calibration -> ES vs GBM EL
│   ├── squeeze_defense.py          # utilization, DTC, IV skew veto
│   └── trs_pricer.py               # TRS Payer on junior tranche, SOFR funding
├── portfolio/
│   ├── mean_cvar.py                # CVXPY
│   └── routing_cuopt.py            # cuOpt for counterparty routing / cardinality
├── agents/
│   ├── llm_client.py               # unified NIM + Claude wrapper
│   ├── graph.py                    # LangGraph state machine
│   ├── state.py                    # PodState TypedDict
│   ├── data_agent.py               # Nemotron-small
│   ├── macro_agent.py              # Nemotron-small, reads BSI + FRED + earnings ASR
│   ├── quant_agent.py              # Nemotron-340B, runs JT + Heston + pricing
│   ├── risk_manager.py             # Nemotron-340B, four-gate + squeeze veto
│   ├── report_agent.py             # generates paper-section updates
│   └── nemo_toolkit_wiring.py      # NeMo Agent Toolkit observability
├── backtest/
│   ├── event_study.py              # Klarna Jul 2022, Affirm Nov 2022, CFPB May 2024, CCD II
│   ├── pnl_sim.py                  # simulated TRS vs equity short
│   └── metrics.py                  # Sharpe, Sortino, max DD, tail metrics
├── dashboard/
│   ├── streamlit_app.py
│   └── next/                       # Next.js + WebSockets (v2)
├── paper/
│   ├── PRELIMINARY_PAPER.md
│   ├── paper.tex
│   ├── figures/
│   └── references.bib
├── notebooks/
├── tests/
└── logs/
    ├── agent_decisions/            # JSONL per run
    └── pod_runs/
\end{lstlisting}

\section{Sprint Sequence (Depth-First, No Time Cap)}

Order is enforced because later sprints depend on earlier outputs. Within each sprint the requirement is \textbf{full rigor, full tests, documented math in docstrings} --- not a minimum viable version.

\subsection{Sprint 0 --- Scaffolding}
\begin{itemize}
  \item \inlinecode{uv init} or \inlinecode{poetry init}, pin Python 3.11.
  \item Install: \inlinecode{duckdb}, \inlinecode{polars}, \inlinecode{pandas}, \inlinecode{numpy}, \inlinecode{scipy}, \inlinecode{statsmodels}, \inlinecode{cvxpy}, \inlinecode{QuantLib}, \inlinecode{langgraph}, \inlinecode{langchain}, \inlinecode{anthropic}, \inlinecode{openai} (for NIM OpenAI-compatible endpoint), \inlinecode{praw}, \inlinecode{pytrends}, \inlinecode{yfinance}, \inlinecode{transformers}, \inlinecode{torch}, \inlinecode{pymilvus}, \inlinecode{streamlit}, \inlinecode{matplotlib}, \inlinecode{pytest}, \inlinecode{python-dotenv}.
  \item \inlinecode{.env.example}: \inlinecode{NVIDIA\_NIM\_API\_KEY}, \inlinecode{ANTHROPIC\_API\_KEY}, \inlinecode{REDDIT\_CLIENT\_ID}, \inlinecode{REDDIT\_CLIENT\_SECRET}, \inlinecode{FRED\_API\_KEY}, \inlinecode{SEC\_EDGAR\_UA} (required by SEC --- real name + email).
  \item Docker-compose for Milvus standalone. Makefile targets. DuckDB schema (\inlinecode{fred\_series}, \inlinecode{sec\_abs\_filings}, \inlinecode{cfpb\_complaints}, \inlinecode{reddit\_posts}, \inlinecode{google\_trends}, \inlinecode{options\_chain}, \inlinecode{short\_interest}, \inlinecode{bsi\_daily}, \inlinecode{pod\_decisions}).
\end{itemize}

\subsection{Sprint A --- Data Layer}
\begin{itemize}
  \item \inlinecode{fred.py}: MOVE, T10Y3M, DRCCLACBS, SOFR as daily series.
  \item \inlinecode{sec\_edgar.py}: \inlinecode{https://efts.sec.gov/LATEST/search-index} JSON API. Rate-limit 10 req/s.
  \item \inlinecode{abs\_parser.py}: extract roll rate to 60+ DPD, excess spread, CNL from each AFRMMT 10-D. Unit-test against three known historical filings.
  \item \inlinecode{cfpb.py}: filter on \inlinecode{product=consumer\_loan}, sub-product $\supseteq$ \{BNPL, Affirm, Klarna, Afterpay, Sezzle, PayPal\}. Daily complaint counts + keyword flags.
  \item \inlinecode{reddit\_praw.py}: subreddits $R = \{$povertyfinance, Debt, personalfinance, Affirm, Klarna$\}$, rate-limit handling, dedup by ID.
  \item \inlinecode{google\_trends.py}: keyword set $K$ (see Paper Appendix C), weekly.
  \item \inlinecode{options\_chain.py}: AFRM, SQ, PYPL daily option-chain snapshots (strike, expiry, IV, volume, OI).
  \item \inlinecode{short\_interest.py}: FINRA bi-monthly + regulatory SHO daily.
  \item \textbf{Test:} \inlinecode{make ingest} end-to-end, DuckDB row counts sanity-check.
\end{itemize}

\subsection{Sprint B --- NLP Layer}
\begin{itemize}
  \item \inlinecode{finbert\_sentiment.py}: HF \inlinecode{ProsusAI/finbert}, batched. Rolling 30-day negative ratio.
  \item \inlinecode{finbert\_tone.py}: \inlinecode{yiyanghkust/finbert-tone} as robustness.
  \item \inlinecode{nlp/rag/ingest\_docs.py}: AFRMMT 10-Ds (3y), Affirm 10-Qs, CFPB May 2024 rule, CCD II. Chunk, embed via NV-EmbedQA, index in Milvus.
  \item Earnings-call ASR: \inlinecode{earnings\_audio.py} $\to$ Parakeet-CTC $\to$ timestamped chunks.
  \item \textbf{Test:} FinBERT output distribution on 100-post sample; RAG recall on known-answer query (``AFRMMT excess spread March 2025?'').
\end{itemize}

\subsection{Sprint C --- Signal Layer (Load-Bearing)}
\textit{The paper rests on this sprint.}
\begin{itemize}
  \item \inlinecode{bsi.py}: z-score each component over rolling 180-day window; weighted composite per \inlinecode{config/weights.yaml}; emit \inlinecode{bsi\_daily}.
  \item \inlinecode{weights\_qp.py}: constrained QP $\min \| \mathrm{BSI} \cdot w - \mathrm{AFRMMT}_{\mathrm{stress}} \|^2$ subject to $w \ge 0$, $\sum w = 1$, per-component caps. Refresh monthly; freeze in OOS windows.
  \item \inlinecode{granger.py}: \inlinecode{statsmodels.tsa.stattools.grangercausalitytests(maxlag=10)} at monthly frequency on AFRMMT 60+ DPD roll rate, excess spread, CNL. Block bootstrap (Politis-Romano 1994) for small-sample-robust $p$-values. Report $F$, $p$, bootstrap CI.
  \item \inlinecode{rolling\_oos.py}: expanding-window refit of BSI weights + Granger on held-out months. Primary defense against small-sample critique ($n \approx 40$).
  \item \textbf{Pre-registration:} commit \inlinecode{hypotheses.md} before running Granger. Lag range 4--8 weeks primary, 1--10 secondary. Reference \S13 of paper.
  \item \textbf{Test:} null-data BSI (white noise) vs real AFRMMT --- Granger should reject at \textasciitilde5\%. Power analysis: document minimum detectable effect given $n = 40$.
\end{itemize}

\subsection{Sprint D --- Quant Layer}
\begin{itemize}
  \item \inlinecode{jarrow\_turnbull.py}: discrete-time reduced-form. $\lambda(t) = \lambda_0 \cdot \exp(\beta_{\mathrm{BSI}} \mathrm{BSI}_t + \beta_{\mathrm{MOVE}} \mathrm{MOVE}_t + \beta_{\mathrm{ES}} \mathrm{ES}_t)$. Recovery $R$ from AFRMMT historical. Monte Carlo 25k paths, antithetic variates. Price junior/mezz/senior at observed attachment/detachment from the most recent AFRMMT supplement. Calibrate $\beta$'s weekly by matching model PV to observed spread.
  \item \inlinecode{heston\_scp.py}: QuantLib \inlinecode{HestonModel} + \inlinecode{HestonModelHelper} calibration to AFRM surface. $\mathrm{SCP} = \mathrm{ES}_{99}^{\mathrm{Heston}} - \mathrm{EL}_{99}^{\mathrm{GBM}}$.
  \item \inlinecode{squeeze\_defense.py}: utilization $= \mathrm{SI} / \mathrm{float}$; DTC $= \mathrm{SI} / \mathrm{ADV}$; 25-$\delta$ IV skew $= \mathrm{IV}(\text{put}, 25\delta) - \mathrm{IV}(\text{call}, 25\delta)$. Veto if utilization $> 0.85$ OR DTC $> 5$ OR skew $>$ historical 90th percentile.
  \item \inlinecode{trs\_pricer.py}: TRS Payer on junior tranche, SOFR + spread funding, Treasury hedge overlay to isolate credit from duration. Mark-to-model weekly.
  \item \textbf{Test:} JT collapses to closed-form constant-$\lambda$ when $\beta$'s $= 0$. Heston calibration RMSE $<$ 3 vol points.
\end{itemize}

\subsection{Sprint E --- Agent Pod}
\begin{itemize}
  \item \inlinecode{llm\_client.py}: \inlinecode{LLMClient(model\_tier: Literal['small','heavy'])}. NIM Nemotron default, Claude fallback on 5xx/timeout. Logs every call.
  \item \inlinecode{state.py}: \inlinecode{PodState} TypedDict with fields \inlinecode{as\_of}, \inlinecode{bsi}, \inlinecode{bsi\_components}, \inlinecode{move}, \inlinecode{scp\_by\_ticker}, \inlinecode{jt\_tranche\_prices}, \inlinecode{squeeze\_metrics}, \inlinecode{ccd\_ii\_days\_remaining}, \inlinecode{gate\_results}, \inlinecode{veto\_reasons}, \inlinecode{trade\_signal}, \inlinecode{agent\_log}.
  \item \inlinecode{graph.py}: LangGraph nodes Data $\to$ Macro $\to$ Quant $\to$ RiskManager $\to$ Report. Risk Manager can loop back to Quant. NeMo Agent Toolkit wiring for audit trail.
  \item Agent responsibilities: Data refreshes DuckDB; Macro reads BSI + FRED + ASR; Quant runs JT + Heston + SCP; Risk Manager enforces four-gate + squeeze; Report generates markdown diffs against \S14 and \S9 of the paper.
  \item \textbf{Test:} dry-run on 2022-07-08 (Klarna down-round week) with cached data; pod emits positive signal; reasoning trace shows BSI spike + MOVE elevation + squeeze check.
\end{itemize}

\subsection{Sprint F --- Portfolio Layer}
\begin{itemize}
  \item \inlinecode{mean\_cvar.py}: CVXPY. Minimize $\mathrm{CVaR}_{\alpha}(-r^\top w)$ subject to leverage cap, per-name cap, cardinality via SOS1 or cuOpt handoff.
  \item \inlinecode{routing\_cuopt.py}: cuOpt handles integer assignment of notional across counterparties with TRS-capacity constraints. Correct use of cuOpt.
\end{itemize}

\subsection{Sprint G --- Backtest}
\begin{itemize}
  \item \inlinecode{event\_study.py}: windows $=$ \{Klarna Jul 2022 down round, Affirm Nov 2022 guidance cut, CFPB May 2024 interpretive rule, each AFRMMT monthly 2023--2025, CCD II deadline Nov 2026 (prospective)\}. CAR on AFRM equity, AFRMMT junior spread move, simulated TRS P\&L. BSI-triggered cohort vs random-trigger control.
  \item \inlinecode{pnl\_sim.py}: deterministic seed. Emits \inlinecode{pnl.csv} + PNGs directly into \inlinecode{paper/figures/}.
  \item \inlinecode{metrics.py}: Sharpe, Sortino, max DD, Calmar, tail ratio, Cornish-Fisher VaR.
\end{itemize}

\subsection{Sprint H --- Reporting}
\begin{itemize}
  \item \inlinecode{make paper}: runs notebooks, refreshes figures, pandoc/LaTeX compile to \inlinecode{paper.pdf}.
  \item Streamlit: Macro Radar (BSI vs AFRMMT excess spread), Squeeze Gauges, Agent Debate Log panel, Execution Hub with ``Approve Trade'' stub.
  \item Next.js port: once Streamlit stable, WebSockets streaming from pod process.
\end{itemize}

\section{Rigor Requirements (The ``Nobel Prize Level'' Bar)}

Six places where taking a shortcut collapses the paper's credibility.

\begin{enumerate}
  \item \textbf{Small-sample Granger.} $n \approx 40$ is insufficient for asymptotic $F$-tests to be trusted. Required: (a) block bootstrap with block length $\sim \sqrt{n}$, 10k replications; (b) rolling OOS; (c) explicit power analysis reporting minimum detectable effect size; (d) pre-registration.
  \item \textbf{BSI weights overfitting.} Weights must be refit only on pre-test data; OOS window is weight-frozen.
  \item \textbf{Jarrow-Turnbull calibration drift.} Refit $\beta$'s weekly but publish the full $\beta$-history in the appendix. Cherry-picking is a known reviewer trap.
  \item \textbf{Heston use-case discipline.} Heston \emph{only} on equity. Do not use Heston $\sigma$ to price ABS. Mistake in original spec; do not revert.
  \item \textbf{Squeeze defense is a hard gate}, not a soft preference. Trades ignoring squeeze defense during high-utilization regime invalidate the framework.
  \item \textbf{TRS P\&L honesty.} Simulated TRS returns must include SOFR funding leg, bid-ask haircut (25--50 bps for junior BNPL tranches), CVA, mark-to-model for illiquid observations. Gross-spread compression $\ne$ P\&L.
\end{enumerate}

\section{Known Traps (Learned During Planning)}

\begin{itemize}
  \item \textbf{cuOpt $\ne$ CVaR solver.} Do not attempt Mean-CVaR on cuOpt.
  \item \textbf{NVIDIA AI-Q is actually the NeMo Agent Toolkit.} Original spec mis-named it.
  \item \textbf{SEC EDGAR has a free documented API} at \inlinecode{efts.sec.gov}. No residential proxies.
  \item \textbf{App Store scraping is blocked.} Apple/Google actively defeat it. Substitute with CFPB keyword frequency until a clean feed appears.
  \item \textbf{Heston-on-ABS is the original spec's biggest error.} Paper explicitly corrects in \S1, \S7, \S8.
  \item \textbf{Nemotron on NIM is hosted, OpenAI-compatible, free with credits.} No TensorRT-LLM self-hosting.
\end{itemize}

\section{Verification Criteria}

The build is ``done'' when all of the following pass:

\begin{enumerate}
  \item \inlinecode{make ingest}: $\ge$3y daily FRED, $\ge$100 AFRMMT filings parsed, $>$10k Reddit posts, weekly Google Trends.
  \item \inlinecode{make bsi}: emits \inlinecode{bsi\_daily} series; figure matches paper \S5.
  \item \inlinecode{make validate}: Granger $F$, $p$, bootstrap CI, rolling OOS. Primary test (BSI $\to$ AFRMMT 60+ DPD, lags 4--8w) reports $p < 0.05$ on at least one roll-rate series --- OR the paper honestly reports the null (acceptable; thesis becomes weaker-form).
  \item \inlinecode{make backtest}: \inlinecode{pnl.csv} + figures. TRS strategy outperforms naive AFRM short in at least one of three event windows.
  \item \inlinecode{make pod}: LangGraph state machine runs end-to-end on most recent tick; emits trade/no-trade with audit trail.
  \item \inlinecode{streamlit run dashboard/streamlit\_app.py}: renders; all panels populate.
  \item \inlinecode{make paper}: rebuilds \inlinecode{paper.pdf}; figures resolve; citations compile.
  \item Fresh \inlinecode{git clone} $\to$ \inlinecode{make setup \&\& make all} runs to completion on a clean machine.
\end{enumerate}

\section{What Already Exists}

\begin{itemize}
  \item \inlinecode{PRELIMINARY\_PAPER.md} (version 0.1, \textasciitilde10{,}000 words). Sections 1--17 + Appendices A/B/C. Methodology-complete. Empirical sections scaffolded awaiting pod output. Khalil (2025) integrated in \S2.4 and \S13.3 (H6).
  \item Memory files at \inlinecode{.claude/projects/.../memory/} documenting scope, architecture, stack, NVIDIA mapping, thesis anchors. Durable across sessions.
\end{itemize}

\section{What to Do First in the Fresh Opus Session}

\begin{enumerate}
  \item Read \inlinecode{PRELIMINARY\_PAPER.md} end-to-end.
  \item Execute \textbf{Sprint 0} (scaffolding) and commit.
  \item Execute \textbf{Sprint A} (data layer) with full tests; longest sprint, foundation for everything.
  \item Execute \textbf{Sprint B} $\to$ \textbf{C} in order. Do not skip to D before C passes --- JT consumes BSI.
  \item After Sprint C passes Granger validation (or honestly reports null), update \S13--\S14 of the paper with actual results.
  \item Proceed D $\to$ E $\to$ F $\to$ G $\to$ H.
  \item Keep paper in-sync with pod at every sprint boundary. \inlinecode{report\_agent.py} emits markdown diffs --- apply them.
\end{enumerate}

\section{Non-Goals (Explicit)}

\begin{itemize}
  \item No real brokerage integration. No ISDA paperwork. No live orders.
  \item No self-hosted LLMs. No TensorRT-LLM. No GPU procurement.
  \item No residential proxies. No App Store scraping.
  \item No claim strategy is deployable as-is. Paper frames it as an institutional research prototype with a ``plug your Tier C data in for $3\times$ amplification'' commercialization pitch.
  \item No Postgres. No Kubernetes. No cloud deployment (local-first).
\end{itemize}

\section{Reference Links}

\begin{itemize}
  \item User benchmark repo: \href{https://github.com/shreejitverma/Adaptive-Volatility-Regime-Based-Execution-and-Risk-Framework}{github.com/shreejitverma/Adaptive-Volatility-Regime-Based-Execution-and-Risk-Framework}
  \item Khalil (2025), \emph{J.\ Modelling in Management}, DOI \href{https://doi.org/10.1108/JM2-08-2025-0415}{10.1108/JM2-08-2025-0415} --- direct methodological precedent.
  \item SEC EDGAR API: \href{https://efts.sec.gov/LATEST/search-index}{efts.sec.gov/LATEST/search-index}
  \item FRED API: \href{https://fred.stlouisfed.org/docs/api/fred/}{fred.stlouisfed.org/docs/api/fred/}
  \item CFPB Complaint DB: \href{https://cfpb.github.io/api/ccdb/}{cfpb.github.io/api/ccdb/}
  \item NVIDIA NIM: \href{https://build.nvidia.com}{build.nvidia.com}
  \item NVIDIA NeMo Agent Toolkit: \href{https://github.com/NVIDIA/NeMo-Agent-Toolkit}{github.com/NVIDIA/NeMo-Agent-Toolkit}
  \item Milvus: \href{https://milvus.io}{milvus.io}
\end{itemize}

\vspace{1em}\hrule\vspace{0.5em}
\noindent\textit{End of masterplan. Paste into Opus, give it filesystem access to the project directory, and instruct it to begin at Sprint 0. Memory files and \inlinecode{PRELIMINARY\_PAPER.md} contain additional detail where needed.}

\end{document}
